---
title: "Pangenome plot comparison"
author: "Julian A Paganini"
date: "2025-12-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyr)
library(broom)
library(dplyr)
library(readxl)
library(reshape2)
library(tidyverse)
library(viridis)
library(stringr)
```

##1. Import data and Wrangle

```{r}
#1. Import all complete genomes data
complete_lengths_subgraphs_id <- read.csv("../results/pangenome_parsed/01_all_complete/length_results.csv")
complete_degree_id <- read.csv("../results/pangenome_parsed/01_all_complete/degree_results.csv")
#combine information
all_complete_data<-left_join(complete_lengths_subgraphs_id,complete_degree_id,by=c("Tool","node_id"="Node"))
#change names
all_complete_data <- all_complete_data %>%
  mutate(
    Tool = recode(
      Tool,
      "pangraph" = "Pangraph",
      "panaroo" = "Panaroo",
      "ppanggolin" = "PPanGGOLiN",
      "ggcaller" = "ggCaller",
      "bifrost" = "Bifrost",
      "cuttlefish" = "Cuttlefish"
      # add more as needed
    )
  )

#Re-order tools
all_complete_data$Tool <- factor(
  all_complete_data$Tool,
  levels = c("Panaroo",
             "PPanGGOLiN",
             "ggCaller",
             "Bifrost",
             "Cuttlefish",
             "Pangraph")
)

all_complete_data$node_id <- gsub("'", "", all_complete_data$node_id)


#Import node abundances
bifrost_abundances_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/bifrost_unitig_id_abundance.tsv", sep="\t")
bifrost_abundances_filt<-bifrost_abundances_filt[,c(177:179)]
#complete for the rest
names(bifrost_abundances_filt)<-c("node_id","n_isolates","fraction_isolates")
bifrost_abundances_filt$Tool<-"Bifrost"
#
cuttlefish_abundances_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/cuttlefish_unitig_id_abundance.csv")
cuttlefish_abundances_filt<-cuttlefish_abundances_filt[,c(1:3)]
names(cuttlefish_abundances_filt) <- c("node_id","n_isolates","fraction_isolates")
cuttlefish_abundances_filt$Tool <- "Cuttlefish"

ggcaller_abundances_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/ggcaller_gene_presence_absence_abundance.tsv", sep="\t")
ggcaller_abundances_filt<-ggcaller_abundances_filt[,c(1,177,178)]
names(ggcaller_abundances_filt) <- c("node_id","n_isolates","fraction_isolates")
ggcaller_abundances_filt$Tool <- "ggCaller"

panaroo_abundances_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/panaroo_gene_presence_absence_abundance.tsv", sep="\t")
panaroo_abundances_filt<-panaroo_abundances_filt[,c(1,177,178)]
names(panaroo_abundances_filt) <- c("node_id","n_isolates","fraction_isolates")
panaroo_abundances_filt$Tool <- "Panaroo"

ppanggolin_abundances_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/ppanggolin_gene_id_abundance.csv")
#add number
ppanggolin_abundances_filt$Gene <- 1:nrow(ppanggolin_abundances_filt)
ppanggolin_abundances_filt<-ppanggolin_abundances_filt[,c(1,3)]
names(ppanggolin_abundances_filt) <- c("node_id","n_isolates")
ppanggolin_abundances_filt$fraction_isolates <- round(ppanggolin_abundances_filt$n_isolates / 175, 9)
ppanggolin_abundances_filt$Tool <- "PPanGGOLiN"


pangraph_abundances_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/pangraph_abundances.tsv")
pangraph_abundances_filt<-pangraph_abundances_filt[,c(1,4,5)]
pangraph_abundances_missing_filt<- read.csv("../../2024_01_pangenome_constructions/results/pangenome_graph/pure_complete/abundances/pangraph_abundances_missing.tsv")
pangraph_abundances_missing_filt<-pangraph_abundances_missing_filt[,c(1,3,4)]
pangraph_abundances_filt<-rbind(pangraph_abundances_filt,pangraph_abundances_missing_filt)
names(pangraph_abundances_filt) <- c("node_id","n_isolates","fraction_isolates")
pangraph_abundances_filt$Tool <- "Pangraph"


all_abundances <- rbind(
  bifrost_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")],
  cuttlefish_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")],
  ggcaller_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")],
  panaroo_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")],
  ppanggolin_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")],
  pangraph_abundances_filt[, c("node_id","n_isolates","fraction_isolates","Tool")]
)


all_complete_data<-left_join(all_complete_data,all_abundances,by=c("Tool","node_id"))

#write.csv(all_complete_data, '../results/Supplementary_table_S6.csv',  row.names = FALSE)

```


##2. PLot complete genome data - 

###2.1 Figure 2A - Node length distribution

```{r fig.width=4, fig.height=5, dpi=300}
#Plot node-length
node_length_distribution <- ggplot(all_complete_data, 
                        aes(x = Tool, y = log(length,10))) +
  geom_violin(aes(fill = Tool),alpha = 0.8, trim = TRUE,scale = "width") +
  geom_boxplot(position = position_dodge(width = 0.8), width = 0.2,outlier.shape = NA) +
  #coord_cartesian(ylim = c(0, 0.3)) +
  theme_minimal() +
  # Uncomment and customize color if needed
  scale_fill_manual(values = c('PPanGGOLiN' = '#FF6600','Panaroo' = '#E00000', "ggCaller"="#D9EB00","Bifrost"="#00BF2F", "Cuttlefish"="#57A303", "Pangraph"="#1F02D4")) +
  theme(
    plot.title = element_text(size = 0, hjust = 0.5, face = 'bold'),
    axis.title.x = element_text(size = 14, face = 'bold'), 
    axis.text.x = element_text(size = 14, angle = 90, vjust=0.5),
    axis.title.y = element_text(size = 14), 
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 0), 
    legend.text = element_text(size = 18), 
    legend.position = 'none'
  ) +
  xlab('') + 
  ylab('log10 (node-length[bp])')

node_length_distribution

```


###2.2 Supplementary table S3 - Node length distribution

```{r}
node_length_dist<-all_complete_data %>% group_by(Tool) %>% summarise(min=min(length), first_quartile=quantile(length,0.25), median=median(length), third_quartile=quantile(length,0.75), max=max(length))
#write.csv(node_length_dist, '../results/Supplementary_table_S3_node_length_dist_complete.csv',  row.names = FALSE)
```

###2.3 Figure 2B (top) - Subgraph size cummulative plot
```{r fig.width=4, fig.height=3, dpi=300}
subgraph_compositions<-all_complete_data %>% group_by(Tool,subgraph_id) %>% summarise(nr_nodes=n(),subgraph_length=sum(length))

subgraph_compositions <- subgraph_compositions %>%
  group_by(Tool) %>%
  mutate(
    total_nodes   = sum(nr_nodes),
    total_length  = sum(subgraph_length),
    frac_nodes    = nr_nodes / total_nodes,
    frac_length   = subgraph_length / total_length
  ) %>%
  ungroup()


# Prepare cumulative data
cdf_data <- subgraph_compositions %>%
  group_by(Tool) %>%
  arrange(desc(frac_nodes), .by_group = TRUE) %>%
  mutate(
    rank = row_number(),              # subgraph rank
    cum_frac_nodes = cumsum(frac_nodes)
  ) %>%
  ungroup()

#write supplementary table S4
#write.csv(cdf_data, '../results/Supplementary_table_S4_subgraph_composition.csv',  row.names = FALSE)

# Plot: all tools in one panel, x = rank, y = cumulative fraction
ggplot(cdf_data, aes(x = rank, y = cum_frac_nodes, colour = Tool)) +
  geom_line(size = 1.2, alpha = 0.9) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1),
    name   = "Cumulative fraction of total graph content"
  ) +
  scale_colour_manual(values = c('PPanGGOLiN' = '#FF6600','Panaroo' = '#E00000', "ggCaller"="#D9EB00","Bifrost"="#00BF2F", "Cuttlefish"="#57A303", "Pangraph"="#1F02D4")) +
  labs(
    x = "Subgraph rank (largest to smallest)",
    title = ""
  ) +
  theme_minimal(base_size = 14) +
  theme(
    panel.grid.minor = element_blank(),
    legend.position = "top",
    legend.title = element_text(size = 0),
    axis.title.x = element_text(size = 12), 
    axis.text.x = element_text(size = 12),
    axis.title.y = element_text(size = 12), 
    axis.text.y = element_text(size = 12),
  )


```

###2.4 Figure 2B (bottom) - Largest connected component fraction

```{r fig.width=4, fig.height=2, dpi=300}
largest_component <- subgraph_compositions %>%
  group_by(Tool) %>%
  summarise(
    largest_frac = max(frac_nodes),
    largest_length_frac = max(frac_length)
  )

ggplot(largest_component, aes(x = Tool, y = largest_frac, fill = Tool)) +
  geom_col(width = 0.7, alpha = 0.8) +
  geom_text(
    aes(label = scales::percent(largest_frac, accuracy = 0.01)),
    vjust = -0.5,
    size = 3
  ) +
  scale_fill_manual(values = c(
    'PPanGGOLiN' = '#FF6600',
    'Panaroo'    = '#E00000',
    'ggCaller'   = '#D9EB00',
    'Bifrost'    = '#00BF2F',
    'Cuttlefish' = '#57A303',
    'Pangraph'   = '#1F02D4'
  )) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 1),
    expand = expansion(mult = c(0, 0.1))  # gives space above bars for the text
  ) +
  labs(
    y = "Fraction (Nodes) in largest subgraph",
    x = "",
    title = ""
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank(),
    legend.title = element_text(size = 0),
    axis.title.x = element_text(size = 12), 
    axis.text.x = element_text(size = 10),
    axis.title.y = element_text(size = 12), 
    axis.text.y = element_text(size = 10),
  )

```

###2.5 Supplementary Figure 1 - Node Degree distribution

```{r fig.width=4, fig.height=6, dpi=300}
node_degree_summary<-all_complete_data %>% group_by(Tool,Degree) %>% summarise(nr_nodes_w_degree=n())

node_degree_summary <- node_degree_summary %>%
  bind_rows(
    tibble(
      Tool = "Cuttlefish",
      Degree = 0,
      nr_nodes_w_degree = 0
    ),
    tibble(
      Tool = "Cuttlefish",
      Degree = 9,
      nr_nodes_w_degree = 0
    ),
    tibble(
      Tool = "Cuttlefish",
      Degree = 10,
      nr_nodes_w_degree = 0
    ),
    tibble(
      Tool = "Bifrost",
      Degree = 9,
      nr_nodes_w_degree = 0
    ),
    tibble(
      Tool = "Bifrost",
      Degree = 10,
      nr_nodes_w_degree = 0
    ),
    tibble(
      Tool = "Pangraph",
      Degree = 1,
      nr_nodes_w_degree = 0
    ),
    tibble(
      Tool = "PPanGGOLiN",
      Degree = 0,
      nr_nodes_w_degree = 0
    )
  )

node_degree_summary <- node_degree_summary %>%
  group_by(Tool) %>%
  mutate(
    total_nodes   = sum(nr_nodes_w_degree),
    perc_nodes_w_degree    = nr_nodes_w_degree / total_nodes
  ) %>%
  ungroup()

node_degree_summary$Tool <- factor(
  node_degree_summary$Tool,
  levels = c("Panaroo",
             "PPanGGOLiN",
             "ggCaller",
             "Bifrost",
             "Cuttlefish",
             "Pangraph")
)

#write.csv(node_degree_summary, '../results/TMP_node_degree_dist.csv',  row.names = FALSE)
node_deg_sub <- node_degree_summary %>%
  filter(Degree <= 10)

total_fraction_deg_10<-node_deg_sub %>% group_by(Tool) %>% summarise(total_percentage=sum(perc_nodes_w_degree))

ggplot(node_deg_sub, aes(x = Degree, y = perc_nodes_w_degree, fill = Tool)) +
  geom_area(alpha = 0.8) +
  geom_text(
    aes(label = scales::percent(perc_nodes_w_degree, accuracy = 0.1)),
    vjust = -0.4,
    size = 3
  ) +
  scale_y_continuous(
    limits = c(0, 0.90),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(breaks = 0:10) +
  labs(
    y = "Percentage of nodes",
    x = "Node degree",
    title = ""
  ) +
  facet_wrap(~ Tool, ncol = 1) +
  scale_fill_manual(values = c(
    'PPanGGOLiN' = '#FF6600',
    'Panaroo'    = '#E00000',
    'ggCaller'   = '#D9EB00',
    'Bifrost'    = '#00BF2F',
    'Cuttlefish' = '#57A303',
    'Pangraph'   = '#1F02D4'
  )) +
  theme_bw() +
  theme(
        legend.position = "none",
        panel.grid.minor = element_blank(),
        legend.title = element_text(size = 0),
        axis.title.x = element_text(size = 12), 
        axis.text.x = element_text(size = 10),
        axis.title.y = element_text(size = 12), 
        axis.text.y = element_text(size = 10),
        strip.text.x = element_text(size = 10)
        )
```

##2.7 Node degree and frequency, normalized per tool

```{r fig.width=7, fig.height=4, dpi=300}

bins <- seq(0, 1, by = 0.05)

df <- all_complete_data %>%
  filter(
    Degree >= 0, Degree <= 10,
    fraction_isolates >= 0, fraction_isolates <= 1
  ) %>%
  mutate(
    degree_bin = Degree,
    frac_bin_raw = cut(fraction_isolates, breaks = bins, include.lowest = TRUE),
    frac_bin = factor(
      frac_bin_raw,
      labels = paste0(seq(0, 95, 5), "%–", seq(5, 100, 5), "%")
    )
  )

# Count per bin per Tool
df_bins <- df %>%
  group_by(Tool, degree_bin, frac_bin) %>%
  summarise(count = n(), .groups = "drop")

# TOTAL COUNTS per tool (correct normalization)
totals <- df %>%
  group_by(Tool) %>%
  summarise(total_nodes = n())

# Normalize by total # nodes of that Tool
df_bins <- df_bins %>%
  left_join(totals, by = "Tool") %>%
  mutate(count_norm = count / total_nodes)


df_bins$Tool <- factor(
  df_bins$Tool,
  levels = c("Panaroo",
             "PPanGGOLiN",
             "ggCaller",
             "Bifrost",
             "Cuttlefish",
             "Pangraph")
)

#write.csv(df_bins, '../results/IMPORTANT_complete_node_degree_normalized_tool.csv',  row.names = FALSE)

# Plot
ggplot(df_bins, aes(x = degree_bin, y = frac_bin, fill = count_norm)) +
  geom_tile() +
  scale_fill_viridis_c(
    name = "Normalized\nnode count",
    limits = c(0, NA)
  ) +
  scale_x_continuous(breaks = 0:10, name = "Node degree") +
  ylab("Fraction of isolates") +
  facet_wrap(~Tool) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(size = 10),
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text.y = element_text(size = 10),
    panel.grid = element_blank(),
    strip.text = element_text(size=12,face = "bold")
  )
```
###2.8 Figure 2C - Node degree and frequency, normalized per node-degree


```{r fig.width=9, fig.height=5, dpi=300}
bins <- seq(0, 1, by = 0.05)

df <- all_complete_data %>%
  filter(
    Degree >= 0, Degree <= 10,
    fraction_isolates >= 0, fraction_isolates <= 1
  ) %>%
  mutate(
    degree_bin = Degree,
    frac_bin_raw = cut(fraction_isolates, breaks = bins, include.lowest = TRUE),
    frac_bin = factor(
      frac_bin_raw,
      labels = paste0(seq(0, 95, 5), "%–", seq(5, 100, 5), "%")
    )
  )


df_bins_node <- df %>%
  group_by(Tool, degree_bin, frac_bin) %>%
  summarise(count = n(), .groups = "drop")

# Normalized - total nodes per Tool & degree
totals_deg <- df %>%
  group_by(Tool, degree_bin) %>%
  summarise(total_deg = n(), .groups = "drop")

totals_nodes <- df %>%
  group_by(Tool) %>%
  summarise(total_nodes = n(), .groups = "drop")

# normalise within Tool × degree
df_bins_node <- df_bins_node %>%
  left_join(totals_deg, by = c("Tool", "degree_bin")) %>%
  mutate(count_norm = count / total_deg)

df_bins_node <- df_bins_node %>%
  left_join(totals_nodes, by = c("Tool")) %>%
  mutate(count_total_norm = count / total_nodes)


#write.csv(df_bins_node, '../results/Supplementary_table_S5.csv',  row.names = FALSE)

df_bins_node$Tool <- factor(
  df_bins_node$Tool,
  levels = c("Panaroo",
             "PPanGGOLiN",
             "ggCaller",
             "Bifrost",
             "Cuttlefish",
             "Pangraph")
)


# Plot
ggplot(df_bins_node, aes(x = degree_bin, y = frac_bin, fill = count_norm)) +
  geom_tile() +
  scale_fill_viridis_c(
    name = "Node fraction\n(Degree normalized)",
    limits = c(0, NA)
  ) +
  scale_x_continuous(breaks = 0:10, name = "Node degree") +
  ylab("Fraction of isolates") +
  facet_wrap(~Tool) +
  theme_bw() +
  theme(
    axis.title.x = element_text(size = 16, face = "bold"),
    axis.text.x = element_text(size = 12),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text.y = element_text(size = 10),
    panel.grid = element_blank(),
    strip.text = element_text(size=16,face = "bold")
  )

```






#OLD CODE



#code
#bar_plot
```{r fig.width=4,fig.height=4, dpi=300}
library(ggplot2)
library(tidyr)
library(dplyr)

gene <- read.csv("../../source_data/pangenome_analysis_and_plot/core_and_accessory.csv")
print(gene)
gene_long <- pivot_longer(gene, cols = c(Core, Accessory), names_to = "Gene_Type", values_to = "Genes_count")

gene_long <- rename(gene_long, Genome_Type = X)

gene_long$Sequence <- factor(gene_long$Sequence,levels=c("Short_read_assembly","Combination_1%_complete","Combination_11%_complete","Combination_50%_complete","Combination_89%_complete","Combination_99%_complete","Complete_genome"))

gene_long$Sequence <- gsub("Short_read_assembly", "0", gene_long$Sequence)
gene_long$Sequence <- gsub("Combination_1%_complete", "1", gene_long$Sequence)
gene_long$Sequence <- gsub("Combination_11%_complete", "10", gene_long$Sequence)
gene_long$Sequence <- gsub("Combination_50%_complete", "50", gene_long$Sequence)
gene_long$Sequence <- gsub("Combination_89%_complete", "90", gene_long$Sequence)
gene_long$Sequence <- gsub("Combination_99%_complete", "99", gene_long$Sequence)
gene_long$Sequence <- gsub("Complete_genome", "100", gene_long$Sequence)


gene_long$Sequence <- factor(gene_long$Sequence, levels = c("0", "1", "10", "50", "90", "99", "100"))

print(gene_long)
# Set Core and Accessory genes at same praph
p <- ggplot(
  data = gene_long,
  mapping = aes(x = Tool, fill = Gene_Type)
) +
  geom_bar(mapping = aes(x = Sequence, y = Genes_count), position = "dodge", stat = "identity", width = 0.5) +
  labs(x = "Percentage of complete genomes", y = "Nr. of Genes") +
  facet_wrap(~ Tool, dir = "v",) +
  theme_bw()+
  scale_fill_manual(values = c("Accessory" = "#274e13", "Core" = "#6aa84f", "Shell" = "#169873"))+
  theme(axis.title.x = element_text(size=18), 
        axis.text.x=element_text(size=16,angle=0),
        axis.title.y=element_text(size=18), 
        axis.text.y=element_text(size=16,angle=0), 
        legend.title = element_text(size = 12), 
        legend.text = element_text(size = 9),
        legend.position='right',
        strip.text.x = element_text(size = 18),
        strip.text.y = element_text(size = 20),
        panel.spacing.y = unit(1, "lines")) 

print(p)
```

#density_plot_bifrost
```{r fig.width=20,fig.height=4}

library(ggplot2)
library(dplyr)

# read data
gene_length <- read.csv("../../source_data/pangenome_analysis_and_plot/merged_bifrost_length_results.csv")

# filter data
filtered_gene_length <- gene_length %>%
  filter(length > 1000 & length < 5000)


options(repr.plot.width=20, repr.plot.height=4)

# create plot
p1 <- ggplot(filtered_gene_length, aes(x = length, color = Source)) + 
  geom_density(alpha = 0.3, size = 1.4) +  
  labs(x = "Node Length (bp)", 
       y = "Density",  
       color = "Source") + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 16),    
    axis.text.y = element_text(size = 16),    
    axis.title.x = element_text(size = 18),   
    axis.title.y = element_text(size = 18),   
    legend.text = element_text(size = 14)     
  )

# 绘制直方图
p2 <- ggplot(filtered_gene_length, aes(x = length, color = Source)) + 
  geom_histogram(bins = 30, size = 0.5) +  
  facet_wrap(~ Source, dir = "h", ncol = 7) +
  labs(x = "Node Length (bp)",  
       y = "Frequency",  
       color = "Source") +  
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 16),    
    axis.text.y = element_text(size = 16),    
    axis.title.x = element_text(size = 18),  
    axis.title.y = element_text(size = 18),   
    legend.text = element_text(size = 14)     
  )

# 显示图形
print(p1)
print(p2)




```
#density_plot_cuttlefish
```{r fig.width=20,fig.height=4}

library(ggplot2)
library(dplyr)

# read data
gene_length <- read.csv("../../source_data/pangenome_analysis_and_plot/merged_cuttlefish_length_results.csv")

# filter data
filtered_gene_length <- gene_length %>%
  filter(length > 1000 & length < 5000)


options(repr.plot.width=20, repr.plot.height=4)

# create plot
p1 <- ggplot(filtered_gene_length, aes(x = length, color = Source)) + 
  geom_density(alpha = 0.3, size = 1.4) +  
  labs(x = "Node Length (bp)", 
       y = "Density",  
       color = "Source") + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 16),    
    axis.text.y = element_text(size = 16),    
    axis.title.x = element_text(size = 18),   
    axis.title.y = element_text(size = 18),   
    legend.text = element_text(size = 14)     
  )

# 绘制直方图
p2 <- ggplot(filtered_gene_length, aes(x = length, color = Source)) + 
  geom_histogram(bins = 30, size = 0.5) +  
  facet_wrap(~ Source, dir = "h", ncol = 7) +
  labs(x = "Node Length (bp)",  
       y = "Frequency",  
       color = "Source") +  
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 16),    
    axis.text.y = element_text(size = 16),    
    axis.title.x = element_text(size = 18),  
    axis.title.y = element_text(size = 18),   
    legend.text = element_text(size = 14)     
  )

# 显示图形
print(p1)
print(p2)

```

# bar plot of edges & nodes
```{r fig.width=10,fig.height=8}
library(ggplot2)
library(tidyr)
library(viridis)
library(dplyr)

# read data
basic_information <- read.csv("../../source_data/pangenome_analysis_and_plot/basic_information.csv")
print(basic_information)

# transfer data
basic_information_change <- pivot_longer(basic_information, cols = c(Node.Count, Edge.Count), names_to = "Basic_Information", values_to = "Count")
print(basic_information_change)


basic_information_change$Percentage.of.Complete.genome <- factor(basic_information_change$Percentage.of.Complete.genome, levels = c("0%", "1%", "10%", "50%", "90%", "99%", "100%"))

# re-ranking tool columns
basic_information_change$Tool <- factor(basic_information_change$Tool, levels = c("panaroo", "PPanGGOLiN", "ggcaller", "bifrost", "cuttlefish", "pangraph"))


ggplot(basic_information_change, aes(x = Percentage.of.Complete.genome, y = Count, fill = Percentage.of.Complete.genome, colour = Percentage.of.Complete.genome)) + 
  geom_bar(position = "dodge", stat = "identity", width = 0.5) +
  scale_fill_manual(values = c("0%" = "#daf8e3", "1%" = "#97ebdb", "11%" = "#00c2c7", "50%" = "#00e9ff", "89%" = "#00b0ff", "99%" = "#0086ad", "100%" = "#005582")) +
  scale_color_manual(values = c("0%" = "#daf8e3", "1%" = "#97ebdb", "11%" = "#00c2c7", "50%" = "#00e9ff", "89%" = "#00b0ff", "99%" = "#0086ad", "100%" = "#005582")) +
  theme_bw() +
  facet_grid(Tool ~ Basic_Information, scales = "free_y") +
  theme(
    plot.title = element_text(size = 0, hjust = 0.5, face = 'bold'),
    axis.title.x = element_text(size = 18), 
    axis.text.x = element_text(size = 13, angle = 0),
    axis.title.y = element_text(size = 18),  # 修改 y 轴标题的大小
    axis.text.y = element_text(size = 12, angle = 0), 
    legend.title = element_text(size = 12), 
    legend.text = element_text(size = 9),
    legend.position = 'none',
    strip.text.x = element_text(size = 15),
    strip.text.y = element_text(size = 12)
  ) +
  labs(y = "Count")  # 添加 y 轴标题





```

# bar plot of subgraphs
```{r fig.width=6,fig.height=8}

library(ggplot2)
library(tidyr)
library(viridis)
library(dplyr)

basic_information_change <- read.csv("../../source_data/pangenome_analysis_and_plot/basic_information.csv")
print(basic_information_change)


basic_information_change$Percentage.of.Complete.genome <- factor(basic_information_change$Percentage.of.Complete.genome,levels=c("0%","1%","10%","50%","90%","99%","100%"))

basic_information_change$Tool <- factor(basic_information_change$Tool,levels=c("bifrost","cuttlefish","panaroo","PPanGGOLiN","ggcaller","pangraph"))

ggplot(basic_information_change, aes(x = Percentage.of.Complete.genome, y = Subgraph.Count, fill = Percentage.of.Complete.genome, colour = Percentage.of.Complete.genome)) + 
  geom_bar(position = "dodge", stat = "identity", width = 0.5) +
  scale_fill_manual(values = c("0%" = "#daf8e3", "1%" = "#97ebdb", "10%" = "#00c2c7", "50%" = "#00e9ff", "90%" = "#00b0ff", "99%" = "#0086ad", "100%" = "#005582")) +
  scale_color_manual(values = c("0%" = "#daf8e3", "1%" = "#97ebdb", "10%" = "#00c2c7", "50%" = "#00e9ff", "90%" = "#00b0ff", "99%" = "#0086ad", "100%" = "#005582")) +
  theme_bw() +
  facet_wrap(~ Tool, scales = "free_y", dir = "v", ncol=1) +
    theme(plot.title = element_text(size=0,hjust = 0.5,face='bold'),
        axis.title.x = element_text(size=18), 
        axis.text.x=element_text(size=13,angle=0),
        axis.title.y=element_text(size=18), 
        axis.text.y=element_text(size=12,angle=0), 
        legend.title = element_text(size = 12), 
        legend.text = element_text(size = 9),
        legend.position='none',
        strip.text.x = element_text(size = 15),
        strip.text.y = element_text(size = 10))+
  labs(y = "Count")  # 添加 y 轴标题


```

#Degree plot just complete genome
```{r fig.width=8,fig.height=10, dpi=300}

library(ggplot2)
library(tidyr)
library(viridis)
library(dplyr)

nodes_degree_complete <- read.delim("../../result/pangenome_analysis_and_plot/pure_complete/degree_results.csv", sep =',')
nodes_degree_complete <- nodes_degree_complete %>% group_by(Tool, Degree) %>% summarise(Node_Count = n())
nodes_degree_complete$fraction <- '100%'

nodes_degree_complete <- nodes_degree_complete %>% group_by(Tool) %>% mutate(total_nodes = sum(Node_Count))
nodes_degree_complete$Node_Fraction <- round(nodes_degree_complete$Node_Count / nodes_degree_complete$total_nodes, 2)

nodes_degree_complete <- nodes_degree_complete[as.integer(nodes_degree_complete$Degree) <= 10,]

nodes_degree_complete

nodes_degree_complete$Tool <- factor(nodes_degree_complete$Tool, levels = c("ggcaller","panaroo", "PPanGGOLiN", "bifrost", "cuttlefish", "pangraph"))

degree_plot_complete <- ggplot(nodes_degree_complete, aes(x = as.integer(Degree), y = Node_Fraction, fill = as.factor(Degree))) +
  geom_bar(stat = 'identity') +
  theme_bw() +
  scale_fill_viridis(discrete = TRUE) +
  theme(
    plot.title = element_text(size = 0, hjust = 0.5, face = 'bold'),
    axis.title.x = element_text(size = 24),  
    axis.text.x = element_text(size = 20, angle = 0),  
    axis.title.y = element_text(size = 24),  
    axis.text.y = element_text(size = 20, angle = 0), 
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 15),
    legend.position = 'none',
    strip.text.x = element_text(size = 24),
    strip.text.y = element_text(size = 18)
  ) +
  labs(fill = '') +
  xlab('Node degree') +
  ylab('Node Fraction') +  
  scale_x_continuous(breaks = seq(0, 10, by = 1)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) +
  facet_wrap(~ Tool, dir = "v", ncol = 1) 

degree_plot_complete





```

# plot of cpu occupied
```{r fig.width=6,fig.height=4, dpi=300}
library(tidyr)
library(dplyr)
library(ggplot2)


base <- read.csv("../../source_data/cpu_memory_occupied/Cup_time_memory.csv")


base$percentage_complete_genome <- factor(base$percentage_complete_genome, levels = c("0%", "1%", "10%", "50%", "90%", "99%", "100%"))

# only save 0%，50%，100%
base_filtered <- base %>% filter(percentage_complete_genome %in% c("0%", "50%", "100%"))


base_long <- pivot_longer(base_filtered, cols = c(Total_cpu_second), names_to = "Metric", values_to = "Value")


custom_colors <- c("#f02943", "#e458aa", "#cd03cc", "#9726eb", "#4c24ea", "#0817af")


ggplot(base_long, aes(x = percentage_complete_genome, y = Value, colour = Tool, group = interaction(Tool, Metric))) +
  geom_line(size = 1, linetype = "dashed") +
  geom_point(size = 3) +  
  ylab('Log [CPU-time (s)]') +
  xlab('Percentage of complete genome') +
  facet_wrap(~ Metric, scales = "free_y") +
  scale_colour_manual(values = custom_colors) +
  scale_y_log10() +  
  theme_minimal() +
  theme(
    axis.line = element_line(color = "black"), 
    axis.title.x = element_text(size = 18),
    axis.text.x=element_text(size=14,angle=0),
    axis.title.y = element_text(size = 18),
    axis.text.y=element_text(size=14,angle=0),
    legend.title= element_text(size = 18),
    legend.text = element_text(size = 18),
  ) 
  




```

# plot of memory occupied
```{r fig.width=6,fig.height=4, dpi=300}
library(tidyr)
library(dplyr)
library(ggplot2)


base <- read.csv("../../source_data/cpu_memory_occupied/Cup_time_memory.csv")


base$percentage_complete_genome <- factor(base$percentage_complete_genome, levels = c("0%", "1%", "10%", "50%", "90%", "99%", "100%"))

# only save 0%，50%，100%
base_filtered <- base %>% filter(percentage_complete_genome %in% c("0%", "50%", "100%"))


base_long <- pivot_longer(base_filtered, cols = c(MaxRSS), names_to = "Metric", values_to = "Value")


custom_colors <- c("#f02943", "#e458aa", "#cd03cc", "#9726eb", "#4c24ea", "#0817af")


ggplot(base_long, aes(x = percentage_complete_genome, y = Value, colour = Tool, group = interaction(Tool, Metric))) +
  geom_line(size = 1, linetype = "dashed") +
  geom_point(size = 3) +  
  ylab('Log [Memory (Bytes)]') +
  xlab('Percentage of complete genome') +
  facet_wrap(~ Metric, scales = "free_y") +
  scale_colour_manual(values = custom_colors) +
  scale_y_log10() +  
  theme_minimal() +
  theme(
    axis.line = element_line(color = "black"), 
    axis.title.x = element_text(size = 18),
    axis.text.x=element_text(size=14,angle=0),
    axis.title.y = element_text(size = 18),
    axis.text.y=element_text(size=14,angle=0),
    legend.title= element_text(size = 20),
    legend.text = element_text(size = 18),
  ) 



```

#PLot Stx-detection

```{r fig.width=12,fig.height=4, dpi=300}
library(ggplot2)
library(tidyr)
library(dplyr)
stx <- read.csv("/home/jpaganini/Predict_Prevent/Benchmark_pangenome_graphs/reproduce_test/benchmarking_pangenome_tools/2024_8_pangenome_benchmark/result/stx/tmp_manual_results_extraction.csv", sep=",", header=TRUE)
stx_plot_poster<-stx[stx$Metric_type=="Complete_stx" |stx$Metric_type=="Fragmented_stx",  ]
stx_plot_poster<-stx_plot_poster[stx_plot_poster$Tools!="Bakta",]
stx_plot_poster_long <- pivot_longer(stx_plot_poster, cols = c(Recall, Precision), names_to = "Metric", values_to = "Value")

custom_colors <- c("#e458aa",  "#9726eb",  "#0817af")

ggplot(stx_plot_poster_long, aes(x = as.factor(Porc_complete_genome), y = Value, colour = Tools)) +
  geom_jitter(size = 3, width = 0.1) +  
  scale_colour_manual(values = custom_colors) +
  theme_bw() +
  theme(
    axis.line = element_line(color = "black"), 
    axis.title.x = element_text(size = 24),
    axis.text.x=element_text(size=20,angle=0),
    axis.title.y = element_text(size = 24),
    axis.text.y=element_text(size=20,angle=0),
    legend.title= element_text(size = 24),
    legend.text = element_text(size = 24),
    strip.text.x = element_text(size = 24),
    strip.text.y = element_text(size = 20),
  ) +
    ylab('Value') +
  xlab('Percentage of complete genomes') +
    facet_grid(Metric_type~ Metric) 
```


